Transfer Learning in Visual and Relational Reasoning\\ (Supplementary Material)

### 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Minor

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
Ahmet S. Ozcan\footnotemark[1] \and \\
IBM Research AI
}

>>>>

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
Tomasz Kornuta\thanks{Currently at NVIDIA. \textit{Santa Clara, CA, USA}.} \and
\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
Emre Sevgen\thanks{Currently at Citrine Informatics.}  \hspace{1cm} \and 
Ahmet S. Ozcan\footnotemark[1] \and \\
IBM Research AI
}

### 2019-11-22 Transfer_Learning/cvpr_submission/appendix.tex
Minor

The combinations of attributes in CoGenT-A and CoGenT-B are shown in~\cref{tab:cogent_conditions_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{cccc}
		\toprule
		Dataset	&	Cubes	&	Cylinders	&	Spheres	\\
		\midrule
		CoGenT-A	&	Gray / Blue / Brown / Yellow	&	Red / Green / Purple / Cyan	&	Any color	\\
		CoGenT-B	&	Red / Green / Purple / Cyan	&	Gray / Blue / Brown / Yellow	&	Any color 	\\
		\bottomrule
	\end{tabular}
	\smallskip
	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
	\label{tab:cogent_conditions_supplement}
\end{table}

The Canonical and Hard variants of the COG dataset~\cite{yang2018dataset} are contrasted in~\cref{tab:cog_variants_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{lcccccc}
		\toprule
		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
		& of   & memory & number of & of & of & of  \\
		& frames & duration & distractors & training set & validation set & test set \\
		\midrule
		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
		\bottomrule	
	\end{tabular}
	\smallskip
	\caption{Details of the Canonical and Hard variants of the COG dataset.}
	\label{tab:cog_variants_supplement}
\end{table}
%
%\begin{table}[ht]
%	\centering
%	\begin{tabular}{lcccccc}.
%		\toprule
%		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
%		& of   & memory & number of & of & of & of 
%%		& frames & duration & distractors & training set & validation set & test set \\
%		\midrule
%		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
%		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
%		\bottomrule	
%	\end{tabular}
%	\caption{Details of the Canonical and Hard variants of the COG dataset.}
%	\label{tab:cog_variants_supplement}
%\end{table}

>>>>

\noindent The combinations of attributes in CoGenT-A and CoGenT-B are shown in~\cref{tab:cogent_conditions_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{cccc}
		\toprule
		Dataset	&	Cubes	&	Cylinders	&	Spheres	\\
		\midrule
		CoGenT-A	&	Gray / Blue / Brown / Yellow	&	Red / Green / Purple / Cyan	&	Any color	\\
		CoGenT-B	&	Red / Green / Purple / Cyan	&	Gray / Blue / Brown / Yellow	&	Any color 	\\
		\bottomrule
	\end{tabular}
	\smallskip
	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
	\label{tab:cogent_conditions_supplement}
\end{table}

\noindent The Canonical and Hard variants of the COG dataset~\cite{yang2018dataset} are contrasted in~\cref{tab:cog_variants_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{lcccccc}
		\toprule
		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
		& of   & memory & number of & of & of & of  \\
		& frames & duration & distractors & training set & validation set & test set \\
		\midrule
		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
		\bottomrule	
	\end{tabular}
	\smallskip
	\caption{Details of the Canonical and Hard variants of the COG dataset.}
	\label{tab:cog_variants_supplement}
\end{table}
%
%\begin{table}[ht]
%	\centering
%	\begin{tabular}{lcccccc}.
%		\toprule
%		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
%		& of   & memory & number of & of & of & of 
%%		& frames & duration & distractors & training set & validation set & test set \\
%		\midrule
%		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
%		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
%		\bottomrule	
%	\end{tabular}
%	\caption{Details of the Canonical and Hard variants of the COG dataset.}
%	\label{tab:cog_variants_supplement}
%\end{table}
